\documentclass[12pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{enumerate}

% info for header block in upper right hand corner
\name{}
\class{Math 45 - Section ---}
\assignment{Homework 2}
\duedate{Friday, March 25, 2016}

\begin{document}

\problemlist{B.\{1,2,3,4,5,6,7,8\}}

\begin{problem}[B1]
    Use integrating factor method to find
    the general solution to the following
    differential equations.

    \begin{enumerate}[(a)]
        \item $2\frac{dy}{dt} + 3y = e^{4t}$
        \item $\frac{dy}{dt} + ty = 5t$
        \item $\frac{1}{x}\frac{dy}{dx} + \frac{1}{x^2}y = e^x$
    \end{enumerate}
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\begin{problem}[B2]
    Find the solution to the initial value problem
    \[
        y' + y = \frac{e^{-t}}{t^2}, \qquad y(1)=0,
    \]
    and explain the behavior of the solution as $t$ 
    tends to $+\infty$.
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\begin{problem}[B3]
    Determine whether or not each of the
    following equations is exact. If it 
    is exact, find the general solution.
    \begin{enumerate}[(a)]
        \item $\frac{dy}{dx} = -\frac{ax+by}{bx+cy}$
        \item $(e^x\sin y + 3y)dx - (3x-e^x\cos y)dy = 0$
    \end{enumerate}
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\begin{problem}[B4]
    \begin{enumerate}[(a)]
        \item Find the general solution to the equation
            \[
                \frac{dy}{dt} = \frac{4\sin(2t)}{y}.
            \]
            Your answer should be an explicit function
            $y(t)$ with two branches.
        \item Now impose the initial condition $y(0) = 1$.
            What is the solution to the DE that satisfies
            this initial condition?
        \item What is the largest $t-$interval on which the
            solution is defined?
    \end{enumerate}
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\begin{problem}[B5]
    Let $f(x, y) = 3x^2 + 2y^2$. Find an exact first
    order differential equation whose solutions are 
    the level curves of $f$.
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\begin{problem}[B6]
    For the last few decades, Italy has had its growth
    rate decline to where soon the country will not even 
    have enough births (or immigration) to replace the
    number of deaths in the country. Thus, its population
    may soon start declining. The population of Italy in
    1950 was 47.1 million, in 1970 it was 53.7 million, and 
    in 1990 it was 56.8 million. 
    
    Consider the non-autonomous Malthusian growth model
    given by the differential equation
    \[
        \frac{dP}{dt} = (at+b)P, \qquad P(1950) = 47.1
    \]
    where the constants a and b are to be determined by the 
    data. Solve this differential equation with the data 
    above. The solution is messy, so you can use a computer
    to deal with arithmetic or linear algebra (but not the 
    differentiation) as long as you show all the steps of 
    your work and explain what you are doing and why. Retain 
    six places after the decimal. (Thanks to Mahaffy for 
    this problem.)
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\begin{problem}[B7]
    You can solve the second order differential equation
    $y'' = y'$ using a change of variables combined with
    separation of variables (or inspection). This simple
    example illustrates a technique that can be applied
    to harder problems. Here’s the idea:
    \begin{itemize}
        \item First define a new variable, $w = y'$.
        \item Rewrite the original DE in terms of $w$ to get $w' = w$.
        \item Solve $w' = w$ to find $w(x)$.
        \item Substitute the answer you get for $w(x)$
            into $w = y'$ and solve for $y$.
        \item Show that your solution satisfies the original DE.
        \item Find the solution that satisfies $y(0) = y'(0) = 1$.
    \end{itemize}
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\begin{problem}[B8]
    Consider the equation
    \begin{align}
        \frac{dy}{dt} &= f(t,y) \label{1}
    \end{align}
    where $f$ and $\frac{\partial f}{\partial y}$ are both
    continuous functions for all real values of t and y. Let
    $y(t)$ and $\tilde{y}(t)$ both be two different solutions
    to (\ref{1}). Explain why the graphs of $y$ and 
    $\tilde{y}$ cannot intersect.
\end{problem}

\begin{solution}
    \vfill
\end{solution}

\end{document}
