\documentclass[12pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{enumerate}

% info for header block in upper right hand corner
\name{}
\class{Math 45 - Section ---}
\assignment{Homework 1}
\duedate{Friday, March 11, 2016}

\newcommand{\RR}{\mathbb{R}}

\begin{document}

\problemlist{1,2,3,4,5,6,7}

%%%%%%%%%%%%%%%%%%
\begin{problem}[1]
    Find the solution to $y' = (1 + x)y^2$, $y(0) = 1$.
    Determine the interval in which the solution
    is defined. Sketch the graph of the solution.
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

%%%%%%%%%%%%%%%%%%
\begin{problem}[2]
    Find the solution to $xdx + ye^{-x}dy = 0$,
    $y(0) = 1$. Determine the interval in which the
    solution is defined. Sketch the graph of the solution.
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

%%%%%%%%%%%%%%%%%%
\begin{problem}[3]
    Find the solution to $y^2(1 - x^2)^{1/2}dy =
    \arcsin(x)dx$, $y(0) = 0$. Determine the interval in
    which the solution is defined. Sketch the graph
    of the solution.
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

%%%%%%%%%%%%%%%%%%
\begin{problem}[4]
    Find the general solution to
    \[
        \text{a) } \frac{dy}{dx} = \frac{x^2+xy+y^2}{x^2}\text{, and b) }\frac{dy}{dx} = \frac{x+3y}{x-y}.
    \]
    \textit{Hint: Use the substitution $y(x) = xv(x)$ to solve for $v(x)$ first.}
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

%%%%%%%%%%%%%%%%%%
\begin{problem}[5]
    Consider the equation
    \begin{align}
        y'+g(t)y = f(t)\label{5-ode}
    \end{align}
    where $f(t)$ and $g(t)$ are continuous functions on
    $\RR$. Let
    \[
        I(t) = \int_0^t g(s)ds.
    \]
    Verify that
    \[
        y(t) = Ce^{-I(t)}+\int_0^t e^{I(s)-I(t)}f(s)ds
    \]
    is a solution to (\ref{5-ode}). What is $y(0)$?
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

%%%%%%%%%%%%%%%%%%
\begin{problem}[6 - Bernoulli's Differential Equation]
    Let $n > 1$ be an integer. Show that the 
    change of variables $z = y^{1-n}$ transforms
    the equation $y' + a(x)y = b(x)y^n$
    into a linear differential equation.
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

%%%%%%%%%%%%%%%%%%
\begin{problem}[7]
    An object (skydiver?) falls off a plane from an
    altitude of 3,000 meters. The gravitational
    force of the earth increases its vertical 
    velocity at a rate of 10 $m$/$sec^2$. After 10 
    seconds a parachute opens causing drag that reduces
    the vertical velocity at a rate of twice the vertical
    velocity.
    \begin{enumerate}[a)]
        \item Find the differential equation for the
            velocity after ten seconds.
        \item Solve the equation in part a)
    \end{enumerate}
\end{problem}

\begin{solution}
    \vfill
\end{solution}
\clearpage

\end{document}
